### 2015-02-20 fundamentals/impl.tex
cite ans paper
significant changes are good. regression tests warn against unexpected, usually backwards incompatible changes

Given a full definition of supply and demand, the \gls{DRE} may be solved either
optimally using a mathematical program or approximately by a simulation-based
heuristic \cite{Gidden2014}. If any trade is denoted as exclusive, e.g., if an
analyst desires an assembly-fidelity model, then either a heuristic must be used
or exchanges must be represented as a \gls{MILP}. If no exclusive trades exist,
a \gls{LP} model may be used. In practice, LPs solve much faster than
\gls{MILP}s. However, both capabilities exist in \Cyclus in order to
provide users with the desired level of fidelity.

@@

Validation, in contrast,  may be defined as the question,
``Is \Cyclus the correct tool?''
Since \Cyclus is alone in its class as an agent-based fuel cycle simulator, longitudinal
validation is not possible. Nonetheless, code-to-code comparisons with fuel cycle
simulators that use other modeling paradigms are underway, if nascent. However, such
exercises are more likely to bring into relief the differences between the modeling
paradigms than supply substantial \gls{QA} and validation.

Lastly, \gls{UQ} is a process that is used on specific simulation
instantiations to statistically determine quality. \gls{UQ} is a process that applies
to the running of many \Cyclus simulations. The kernel itself, as a generic fuel cycle
simulator, cannot make reliable statements about the uncertainty of a particular fuel
cycle. Any \gls{UQ} results are applicable only to the scenario that is under
analysis by the user. \Cyclus is not a panacea for due diligence on behalf of the fuel
cycle modeler. Thus, \gls{UQ} is envisioned to be beyond the scope of core development
and in the domain of the expert user.

@@

\Cyclus uses the Google Test framework \cite{inc_googletest_2008} as a harness for running unit
tests. Sufficient unit tests are required for any proposed change to the \Cyclus
code base. Currently \Cyclus implements over 450 unit tests and \Cycamore implements
85.  These cover approximately 65\% of their respective code bases, and their numbers are expected to grow over time.

@@

Regression tests ensure significant changes do not
occur over the course of \Cyclus development. Such a change is called a
\emph{regression} because the new version is almost always wrong.
Regression tests are implemented similarly to integration tests.
Nose is used to execute full \Cyclus simulations whose results
are then compared. In this category, however, the comparison is done against
the output of the same input file when run with a previous version of \Cyclus,
typically the last released version.
In some sense, regression tests are `dumb' in that they do
not care about the contents of a simulation being correct, only whether or not
it changed. They pick up glaring time-sensitive mistakes that may
not appear elsewhere, though they do not purport to make claims about the
quality of the physics modeled. Regression tests are primarily implemented
in \Cycamore because its archetypes are sophisticated enough
to make interesting input files. Only a handful ($<10$) of time steps are needed
for regression testing.

>>>>

Given a full definition of supply and demand, the \gls{DRE} may be solved either
optimally using a mathematical program or approximately by a simulation-based
heuristic \cite{gidden_agent-based_2014}. If any trade is denoted as exclusive, e.g., if an
analyst desires an assembly-fidelity model, then either a heuristic must be used
or exchanges must be represented as a \gls{MILP}. If no exclusive trades exist,
a \gls{LP} model may be used. In practice, LPs solve much faster than
\gls{MILP}s. However, both capabilities exist in \Cyclus in order to
provide users with the desired level of fidelity.

@@

Validation, in contrast,  may be defined as the question,
``Is \Cyclus the correct tool?''
Since \Cyclus is alone in its class as an agent-based fuel cycle simulator, longitudinal
validation is not possible. Nonetheless, code-to-code comparisons with fuel cycle
simulators that use other modeling paradigms are underway
\cite{huff_extensions_2014}. However, such
exercises are more likely to bring into relief the differences between the modeling
paradigms than supply substantial \gls{QA} and validation.

Lastly, \gls{UQ} is a process that is used on specific simulation
instantiations to statistically determine quality. \gls{UQ} is a process that applies
to the running of many \Cyclus simulations. The kernel itself, as a generic fuel cycle
simulator, cannot make reliable statements about the uncertainty of metrics for a particular fuel
cycle. Any \gls{UQ} results are applicable only to the scenario that is under
analysis by the user. \Cyclus is not a substitute for due diligence on behalf of the fuel
cycle modeler. Thus, \gls{UQ} is envisioned to be beyond the scope of core development
and in the domain of the expert user.

@@

\Cyclus uses the Google Test framework \cite{inc_googletest_2008} as a harness for running unit
tests. Sufficient unit tests are required for any proposed change to the \Cyclus
code base. Currently, \Cyclus implements over 450 unit tests and \Cycamore implements
85.  These cover approximately 65\% of their respective code bases, and these numbers are expected to grow over time.

@@

Regression tests ensure unexpected backwards-incompatible changes do not
occur over the course of \Cyclus development. Such a change is called a
\emph{regression} because the new version is almost always wrong.
Regression tests are implemented similarly to integration tests.
Nose is used to execute full \Cyclus simulations whose results
are then compared. In this category, however, the comparison is done against
the output of the same input file when run with a previous version of \Cyclus,
typically the last released version.
In some sense, regression tests are `dumb' in that they do
not care about the contents of a simulation being correct, only whether or not
it changed. They pick up glaring time-sensitive mistakes that may
not appear elsewhere, though they do not purport to make claims about the
quality of the physics modeled. Regression tests are primarily implemented
in \Cycamore because its archetypes are sophisticated enough
to make interesting input files. Only a handful ($<10$) of time steps are needed
for regression testing.
